---
title: "World Chef - LTV Extrapolated"
author: "Sociapoint - Strategic Analytics - Ricard Martinez"
date: "26 de abril de 2016"
output: pdf_document
---

# WORLD CHEF IOS
## This document contains the LTV Extrapolated for World Chef. The analysis contains the 180 Days extrapolation for:

###- All Marketing data without Facebook
###- The results are based on the Logarithmic regression based on the RPI (Revenues per Install).
###- Only using data of the 6 previous months.

###- All marketing countries (US,UK,CA,AU,DE,FR)

```{r, echo =FALSE}
#Connecting to the database
#install.packages("RPostgreSQL")
library(RPostgreSQL)
library(DBI)
library(ggplot2)
drv <- dbDriver("PostgreSQL")
spdb <- dbConnect(
  drv,
  host = "sp-rc.cm7gsqupavgd.us-east-1.redshift.amazonaws.com",
  port = "5439",
  dbname = "datawarehouse",
  user = "rmartinez",
  password = "Shishishi0"
)
```
\newpage

# WORLD CHEF IOS US
## WC - IOS - US - Marketing w/o Facebook

### SQL CODE
```{r, echo=TRUE}
sql_wc_ios_US_marketing_not_fb = "
       select d_cohort,
       rpi
from (select rank() over (order by date (date_register_ios) desc) d_cohort,
             date (date_register_ios) d_date,
             nvl (sum(revenues_dollars_net) / count(distinct user_id),0) as rpi
      from restaurantcity.t_user
      where date_register_ios is not null
      and   date_register_ios >= '2016-01-14'
      and   migrate_date_orphaned is null
      and   register_source_type = 'marketing'
      and   register_ip_country = 'US'
      and   LOWER (register_source) not like '%facebook%'
      group by d_date
      order by d_date desc)
order by 1 asc"
```

### CHART
```{r, echo=FALSE}
data_wc_ios_US_marketing_not_fb <- dbGetQuery(spdb,sql_wc_ios_US_marketing_not_fb);
Data <- data_wc_ios_US_marketing_not_fb;

nls_fit <- nls(rpi~a+d_cohort^b, Data, start = list(a = 1, b = 1))
predicted<-predict(nls_fit,newdata=list(d_cohort=seq(1,365,by=1)), interval="prediction")

Data <- data_wc_ios_US_marketing_not_fb
Data$logCohort<-log(Data$d_cohort)
model<-lm(rpi ~ logCohort, data = Data)
plot(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n", type="n")
for(x in seq(0,180, by=5)) abline(v=x, col="grey")
for(x in seq(0,as.integer(max(Data$rpi))+1,by=0.25)) abline(h=x, col="grey")
points(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n")
axis(1,seq(0,180,by=5),seq(0,180,by=5), cex.axis=0.6)
axis(2,seq(0,as.integer(max(Data$rpi))+1,by=0.25),seq(0,as.integer(max(Data$rpi))+1,by=0.25), cex.axis=0.6)
v180d <- predict(model, newdata = data.frame(logCohort = log(1:365)))
lines(1:180, v180d[1:180], col="blue", lwd=2)
lines(1:180, predicted[1:180], col = "red", lwd=2)
linearCoef<-round(model$coefficients, digits=2)
expCoef<-round(coefficients(nls_fit),digits=2)
rsquaredLog<-round(summary(model)$r.squared,digits=2)
rsquaredExp<-round(summary(lm(Data$rpi ~ predicted[1:nrow(Data)]))$r.squared, digits=2)
legend("topright",legend=c(paste0("y = ", linearCoef[1], " + ", linearCoef[2],"*ln(x)\nR-squared: ", rsquaredLog, "\n"), paste0("y = ", expCoef[1], " + ","x^",expCoef[2],"\nR-squared: ", rsquaredExp,"\n")),lty=1,col=c("blue","red"),lwd=2, cex = 0.6,bg ="white" )

```
\newpage

## WC - IOS - US - Marketing w/o Facebook

### RESULTS

#### LOGARITHMIC
```{r, echo=FALSE}
cat("R-squared : ", rsquaredLog)
cat("Formula: ", model$coefficients[1], " + ", model$coefficients[2],"ln(x) ",sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", v180d[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", v180d[180])
cat("LTV Extrapolated 365 Days: ", v180d[365])
```


#### EXPONENTIAL
```{r, echo=FALSE}
cat("R-squared : ", rsquaredExp)
cat("Formula: ", "y = ", expCoef[1], " + ","x^",expCoef[2],sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", predicted[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", predicted[180])
cat("LTV Extrapolated 365 Days: ", predicted[365])
```

\newpage

# WORLD CHEF IOS GB
## WC - IOS - GB - Marketing w/o Facebook

### SQL CODE
```{r, echo=TRUE}
sql_wc_ios_GB_marketing_not_fb = "
       select d_cohort,
       rpi
from (select rank() over (order by date (date_register_ios) desc) d_cohort,
             date (date_register_ios) d_date,
             nvl (sum(revenues_dollars_net) / count(distinct user_id),0) as rpi
      from restaurantcity.t_user
      where date_register_ios is not null
      and   date_register_ios >= '2016-01-14'
      and   migrate_date_orphaned is null
      and   register_source_type = 'marketing'
      and   register_ip_country = 'GB'
      and   LOWER (register_source) not like '%facebook%'
      group by d_date
      order by d_date desc)
order by 1 asc"
```

### CHART
```{r, echo=FALSE}
data_wc_ios_GB_marketing_not_fb <- dbGetQuery(spdb,sql_wc_ios_GB_marketing_not_fb);
Data <- data_wc_ios_GB_marketing_not_fb;

nls_fit <- nls(rpi~a+d_cohort^b, Data, start = list(a = 1, b = 1))
predicted<-predict(nls_fit,newdata=list(d_cohort=seq(1,365,by=1)), interval="prediction")

Data <- data_wc_ios_GB_marketing_not_fb
Data$logCohort<-log(Data$d_cohort)
model<-lm(rpi ~ logCohort, data = Data)
plot(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n", type="n")
for(x in seq(0,180, by=5)) abline(v=x, col="grey")
for(x in seq(0,as.integer(max(Data$rpi))+1,by=0.25)) abline(h=x, col="grey")
points(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n")
axis(1,seq(0,180,by=5),seq(0,180,by=5), cex.axis=0.6)
axis(2,seq(0,as.integer(max(Data$rpi))+1,by=0.25),seq(0,as.integer(max(Data$rpi))+1,by=0.25), cex.axis=0.6)
v180d <- predict(model, newdata = data.frame(logCohort = log(1:365)))
lines(1:180, v180d[1:180], col="blue", lwd=2)
lines(1:180, predicted[1:180], col = "red", lwd=2)
linearCoef<-round(model$coefficients, digits=2)
expCoef<-round(coefficients(nls_fit),digits=2)
rsquaredLog<-round(summary(model)$r.squared,digits=2)
rsquaredExp<-round(summary(lm(Data$rpi ~ predicted[1:nrow(Data)]))$r.squared, digits=2)
legend("topright",legend=c(paste0("y = ", linearCoef[1], " + ", linearCoef[2],"*ln(x)\nR-squared: ", rsquaredLog, "\n"), paste0("y = ", expCoef[1], " + ","x^",expCoef[2],"\nR-squared: ", rsquaredExp,"\n")),lty=1,col=c("blue","red"),lwd=2, cex = 0.6,bg ="white" )

```
\newpage

## WC - IOS - GB - Marketing w/o Facebook
### RESULTS


#### LOGARITHMIC
```{r, echo=FALSE}
cat("R-squared : ", rsquaredLog)
cat("Formula: ", model$coefficients[1], " + ", model$coefficients[2],"ln(x) ",sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", v180d[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", v180d[180])
cat("LTV Extrapolated 365 Days: ", v180d[365])
```


####EXPONENTIAL
```{r, echo=FALSE}
cat("R-squared : ", rsquaredExp)
cat("Formula: ", "y = ", expCoef[1], " + ","x^",expCoef[2],sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", predicted[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", predicted[180])
cat("LTV Extrapolated 365 Days: ", predicted[365])
```

\newpage

# WORLD CHEF IOS CA
## WC - IOS - CA - Marketing w/o Facebook

### SQL CODE
```{r, echo=TRUE}
sql_wc_ios_CA_marketing_not_fb = "
       select d_cohort,
       rpi
from (select rank() over (order by date (date_register_ios) desc) d_cohort,
             date (date_register_ios) d_date,
             nvl (sum(revenues_dollars_net) / count(distinct user_id),0) as rpi
      from restaurantcity.t_user
      where date_register_ios is not null
      and   date_register_ios >= '2016-01-14'
      and   migrate_date_orphaned is null
      and   register_source_type = 'marketing'
      and   register_ip_country = 'CA'
      and   LOWER (register_source) not like '%facebook%'
      group by d_date
      order by d_date desc)
order by 1 asc"
```

### CHART
```{r, echo=FALSE}
data_wc_ios_CA_marketing_not_fb <- dbGetQuery(spdb,sql_wc_ios_CA_marketing_not_fb);
Data <- data_wc_ios_CA_marketing_not_fb;

nls_fit <- nls(rpi~a+d_cohort^b, Data, start = list(a = 1, b = 1))
predicted<-predict(nls_fit,newdata=list(d_cohort=seq(1,365,by=1)), interval="prediction")

Data <- data_wc_ios_CA_marketing_not_fb
Data$logCohort<-log(Data$d_cohort)
model<-lm(rpi ~ logCohort, data = Data)
plot(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n", type="n")
for(x in seq(0,180, by=5)) abline(v=x, col="grey")
for(x in seq(0,as.integer(max(Data$rpi))+1,by=0.25)) abline(h=x, col="grey")
points(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n")
axis(1,seq(0,180,by=5),seq(0,180,by=5), cex.axis=0.6)
axis(2,seq(0,as.integer(max(Data$rpi))+1,by=0.25),seq(0,as.integer(max(Data$rpi))+1,by=0.25), cex.axis=0.6)
v180d <- predict(model, newdata = data.frame(logCohort = log(1:365)))
lines(1:180, v180d[1:180], col="blue", lwd=2)
lines(1:180, predicted[1:180], col = "red", lwd=2)
linearCoef<-round(model$coefficients, digits=2)
expCoef<-round(coefficients(nls_fit),digits=2)
rsquaredLog<-round(summary(model)$r.squared,digits=2)
rsquaredExp<-round(summary(lm(Data$rpi ~ predicted[1:nrow(Data)]))$r.squared, digits=2)
legend("topright",legend=c(paste0("y = ", linearCoef[1], " + ", linearCoef[2],"*ln(x)\nR-squared: ", rsquaredLog, "\n"), paste0("y = ", expCoef[1], " + ","x^",expCoef[2],"\nR-squared: ", rsquaredExp,"\n")),lty=1,col=c("blue","red"),lwd=2, cex = 0.6,bg ="white" )

```
\newpage

## WC - IOS - CA - Marketing w/o Facebook
### RESULTS


#### LOGARITHMIC
```{r, echo=FALSE}
cat("R-squared : ", rsquaredLog)
cat("Formula: ", model$coefficients[1], " + ", model$coefficients[2],"ln(x) ",sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", v180d[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", v180d[180])
cat("LTV Extrapolated 365 Days: ", v180d[365])
```


####EXPONENTIAL
```{r, echo=FALSE}
cat("R-squared : ", rsquaredExp)
cat("Formula: ", "y = ", expCoef[1], " + ","x^",expCoef[2],sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", predicted[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", predicted[180])
cat("LTV Extrapolated 365 Days: ", predicted[365])
```

\newpage

# WORLD CHEF IOS AU
## WC - IOS - AU - Marketing w/o Facebook

### SQL CODE
```{r, echo=TRUE}
sql_wc_ios_AU_marketing_not_fb = "
       select d_cohort,
       rpi
from (select rank() over (order by date (date_register_ios) desc) d_cohort,
             date (date_register_ios) d_date,
             nvl (sum(revenues_dollars_net) / count(distinct user_id),0) as rpi
      from restaurantcity.t_user
      where date_register_ios is not null
      and   date_register_ios >= '2016-01-14'
      and   migrate_date_orphaned is null
      and   register_source_type = 'marketing'
      and   register_ip_country = 'AU'
      and   LOWER (register_source) not like '%facebook%'
      group by d_date
      order by d_date desc)
order by 1 asc"
```

### CHART
```{r, echo=FALSE}
data_wc_ios_AU_marketing_not_fb <- dbGetQuery(spdb,sql_wc_ios_AU_marketing_not_fb);
Data <- data_wc_ios_AU_marketing_not_fb;

nls_fit <- nls(rpi~a+d_cohort^b, Data, start = list(a = 1, b = 1))
predicted<-predict(nls_fit,newdata=list(d_cohort=seq(1,365,by=1)), interval="prediction")

Data <- data_wc_ios_AU_marketing_not_fb
Data$logCohort<-log(Data$d_cohort)
model<-lm(rpi ~ logCohort, data = Data)
plot(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n", type="n")
for(x in seq(0,180, by=5)) abline(v=x, col="grey")
for(x in seq(0,as.integer(max(Data$rpi))+1,by=0.25)) abline(h=x, col="grey")
points(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n")
axis(1,seq(0,180,by=5),seq(0,180,by=5), cex.axis=0.6)
axis(2,seq(0,as.integer(max(Data$rpi))+1,by=0.25),seq(0,as.integer(max(Data$rpi))+1,by=0.25), cex.axis=0.6)
v180d <- predict(model, newdata = data.frame(logCohort = log(1:365)))
lines(1:180, v180d[1:180], col="blue", lwd=2)
lines(1:180, predicted[1:180], col = "red", lwd=2)
linearCoef<-round(model$coefficients, digits=2)
expCoef<-round(coefficients(nls_fit),digits=2)
rsquaredLog<-round(summary(model)$r.squared,digits=2)
rsquaredExp<-round(summary(lm(Data$rpi ~ predicted[1:nrow(Data)]))$r.squared, digits=2)
legend("topright",legend=c(paste0("y = ", linearCoef[1], " + ", linearCoef[2],"*ln(x)\nR-squared: ", rsquaredLog, "\n"), paste0("y = ", expCoef[1], " + ","x^",expCoef[2],"\nR-squared: ", rsquaredExp,"\n")),lty=1,col=c("blue","red"),lwd=2, cex = 0.6,bg ="white" )

```
\newpage

## WC - IOS - AU - Marketing w/o Facebook
### RESULTS


#### LOGARITHMIC
```{r, echo=FALSE}
cat("R-squared : ", rsquaredLog)
cat("Formula: ", model$coefficients[1], " + ", model$coefficients[2],"ln(x) ",sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", v180d[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", v180d[180])
cat("LTV Extrapolated 365 Days: ", v180d[365])
```


####EXPONENTIAL
```{r, echo=FALSE}
cat("R-squared : ", rsquaredExp)
cat("Formula: ", "y = ", expCoef[1], " + ","x^",expCoef[2],sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", predicted[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", predicted[180])
cat("LTV Extrapolated 365 Days: ", predicted[365])
```

\newpage

# WORLD CHEF IOS FR
## WC - IOS - FR - Marketing w/o Facebook

### SQL CODE
```{r, echo=TRUE}
sql_wc_ios_FR_marketing_not_fb = "
       select d_cohort,
       rpi
from (select rank() over (order by date (date_register_ios) desc) d_cohort,
             date (date_register_ios) d_date,
             nvl (sum(revenues_dollars_net) / count(distinct user_id),0) as rpi
      from restaurantcity.t_user
      where date_register_ios is not null
      and   date_register_ios >= '2016-01-14'
      and   migrate_date_orphaned is null
      and   register_source_type = 'marketing'
      and   register_ip_country = 'FR'
      and   LOWER (register_source) not like '%facebook%'
      group by d_date
      order by d_date desc)
order by 1 asc"
```

### CHART
```{r, echo=FALSE}
data_wc_ios_FR_marketing_not_fb <- dbGetQuery(spdb,sql_wc_ios_FR_marketing_not_fb);
Data <- data_wc_ios_FR_marketing_not_fb;

nls_fit <- nls(rpi~a+d_cohort^b, Data, start = list(a = 1, b = 1))
predicted<-predict(nls_fit,newdata=list(d_cohort=seq(1,365,by=1)), interval="prediction")

Data <- data_wc_ios_FR_marketing_not_fb
Data$logCohort<-log(Data$d_cohort)
model<-lm(rpi ~ logCohort, data = Data)
plot(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n", type="n")
for(x in seq(0,180, by=5)) abline(v=x, col="grey")
for(x in seq(0,as.integer(max(Data$rpi))+1,by=0.25)) abline(h=x, col="grey")
points(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n")
axis(1,seq(0,180,by=5),seq(0,180,by=5), cex.axis=0.6)
axis(2,seq(0,as.integer(max(Data$rpi))+1,by=0.25),seq(0,as.integer(max(Data$rpi))+1,by=0.25), cex.axis=0.6)
v180d <- predict(model, newdata = data.frame(logCohort = log(1:365)))
lines(1:180, v180d[1:180], col="blue", lwd=2)
lines(1:180, predicted[1:180], col = "red", lwd=2)
linearCoef<-round(model$coefficients, digits=2)
expCoef<-round(coefficients(nls_fit),digits=2)
rsquaredLog<-round(summary(model)$r.squared,digits=2)
rsquaredExp<-round(summary(lm(Data$rpi ~ predicted[1:nrow(Data)]))$r.squared, digits=2)
legend("topright",legend=c(paste0("y = ", linearCoef[1], " + ", linearCoef[2],"*ln(x)\nR-squared: ", rsquaredLog, "\n"), paste0("y = ", expCoef[1], " + ","x^",expCoef[2],"\nR-squared: ", rsquaredExp,"\n")),lty=1,col=c("blue","red"),lwd=2, cex = 0.6,bg ="white" )

```
\newpage

## WC - IOS - FR - Marketing w/o Facebook
### RESULTS


#### LOGARITHMIC
```{r, echo=FALSE}
cat("R-squared : ", rsquaredLog)
cat("Formula: ", model$coefficients[1], " + ", model$coefficients[2],"ln(x) ",sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", v180d[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", v180d[180])
cat("LTV Extrapolated 365 Days: ", v180d[365])
```


####EXPONENTIAL
```{r, echo=FALSE}
cat("R-squared : ", rsquaredExp)
cat("Formula: ", "y = ", expCoef[1], " + ","x^",expCoef[2],sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", predicted[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", predicted[180])
cat("LTV Extrapolated 365 Days: ", predicted[365])
```

\newpage

# WORLD CHEF IOS DE
## WC - IOS - DE - Marketing w/o Facebook

### SQL CODE
```{r, echo=TRUE}
sql_wc_ios_DE_marketing_not_fb = "
       select d_cohort,
       rpi
from (select rank() over (order by date (date_register_ios) desc) d_cohort,
             date (date_register_ios) d_date,
             nvl (sum(revenues_dollars_net) / count(distinct user_id),0) as rpi
      from restaurantcity.t_user
      where date_register_ios is not null
      and   date_register_ios >= '2016-01-14'
      and   migrate_date_orphaned is null
      and   register_source_type = 'marketing'
      and   register_ip_country = 'DE'
      and   LOWER (register_source) not like '%facebook%'
      group by d_date
      order by d_date desc)
order by 1 asc"
```

### CHART
```{r, echo=FALSE}
data_wc_ios_DE_marketing_not_fb <- dbGetQuery(spdb,sql_wc_ios_DE_marketing_not_fb);
Data <- data_wc_ios_DE_marketing_not_fb;

nls_fit <- nls(rpi~a+d_cohort^b, Data, start = list(a = 1, b = 1))
predicted<-predict(nls_fit,newdata=list(d_cohort=seq(1,365,by=1)), interval="prediction")

Data <- data_wc_ios_DE_marketing_not_fb
Data$logCohort<-log(Data$d_cohort)
model<-lm(rpi ~ logCohort, data = Data)
plot(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n", type="n")
for(x in seq(0,180, by=5)) abline(v=x, col="grey")
for(x in seq(0,as.integer(max(Data$rpi))+1,by=0.25)) abline(h=x, col="grey")
points(1:nrow(Data), Data$rpi, xlim=c(0,180), ylim=c(0,max(Data$rpi)), pch=16, xlab="Days since register", ylab="RPI + LTV Extrapolated", xaxt="n",yaxt="n")
axis(1,seq(0,180,by=5),seq(0,180,by=5), cex.axis=0.6)
axis(2,seq(0,as.integer(max(Data$rpi))+1,by=0.25),seq(0,as.integer(max(Data$rpi))+1,by=0.25), cex.axis=0.6)
v180d <- predict(model, newdata = data.frame(logCohort = log(1:365)))
lines(1:180, v180d[1:180], col="blue", lwd=2)
lines(1:180, predicted[1:180], col = "red", lwd=2)
linearCoef<-round(model$coefficients, digits=2)
expCoef<-round(coefficients(nls_fit),digits=2)
rsquaredLog<-round(summary(model)$r.squared,digits=2)
rsquaredExp<-round(summary(lm(Data$rpi ~ predicted[1:nrow(Data)]))$r.squared, digits=2)
legend("topright",legend=c(paste0("y = ", linearCoef[1], " + ", linearCoef[2],"*ln(x)\nR-squared: ", rsquaredLog, "\n"), paste0("y = ", expCoef[1], " + ","x^",expCoef[2],"\nR-squared: ", rsquaredExp,"\n")),lty=1,col=c("blue","red"),lwd=2, cex = 0.6,bg ="white" )

```
\newpage

## WC - IOS - DE - Marketing w/o Facebook
### RESULTS


#### LOGARITHMIC
```{r, echo=FALSE}
cat("R-squared : ", rsquaredLog)
cat("Formula: ", model$coefficients[1], " + ", model$coefficients[2],"ln(x) ",sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", v180d[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", v180d[180])
cat("LTV Extrapolated 365 Days: ", v180d[365])
```


####EXPONENTIAL
```{r, echo=FALSE}
cat("R-squared : ", rsquaredExp)
cat("Formula: ", "y = ", expCoef[1], " + ","x^",expCoef[2],sep="")
cat("LTV Extrapolated ", nrow(Data), " Days: ", predicted[nrow(Data)], sep="")
cat("LTV Extrapolated 180 Days: ", predicted[180])
cat("LTV Extrapolated 365 Days: ", predicted[365])
```
